---
title: Comparing Olex and OV navigational systems for Offshore Scallop Survey
output: html_document
editor_options: 
  chunk_output_type: console
---
### Comparisons to prepare for transition to Olex

Comparative tow tracking occured on Middle, Browns North, Georges Bank Monitoring Stations, and German Bank in Spring 2022. 

```{r, echo=F, include=F}
# read in functions and load packages
funs <- c("https://raw.githubusercontent.com/freyakeyser/Assessment_fns/master/Survey_and_OSAC/getdis.r",
          "https://raw.githubusercontent.com/freyakeyser/Assessment_fns/master/Survey_and_OSAC/olex_import.R")
# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
for(fun in funs) 
{
  download.file(fun,destfile = basename(fun))
  source(paste0(getwd(),"/",basename(fun)))
  file.remove(paste0(getwd(),"/",basename(fun)))
} 

require(sf)
require(dplyr)
require(tidyverse)
require(plotly)
require(lubridate)
```

```{r, echo=F, include=F, eval=F}
# Starting with OV, grab the folder names in which the logs are saved

folders <- c("LE15BBNlog", "LE15BBNextralog", "LE15GBMonlog", "LE15GERlog", "Middlelogs"
  )

# now we're going to loop through the OV log files applying both the getdis function, and mave calculations in order to do high-res comparisons
ovd_raw <- NULL 
ovd_track <- NULL
ovd_se <- NULL
ovd_mave <- NULL
mave1 <- NULL
for(i in folders){
  print(i)
  
  ## OLD WAY
  townums <- gsub(x=list.files(paste0("Y:/Offshore/Assessment/Data/Survey_data/2022/Database loading/LE15/", i, "/")), pattern=".log", replacement="")
  #if(any(townums=="440")) townums <- townums[!townums %in% c("440", "450")]
  ovd_sub <- dist.coef(tows=townums, 
                       path=paste0("Y:/Offshore/Assessment/Data/Survey_data/2022/Database loading/LE15/", i, "/"),
                       w=c(1:10,9:1),rule=8,smooth=T,plt=F)
  ovd_sub[[2]]$folder <- i
  ovd_sub[[1]]$PID <- 1:nrow(ovd_sub[[1]])
  ovd_sub[[2]] <- left_join(ovd_sub[[2]], ovd_sub[[1]][, c("PID", "tow")])
  
  ovd_track <- rbind(ovd_track, ovd_sub[[2]])
  ovd_se <- rbind(ovd_se, ovd_sub[[1]])
  
  # using sf and mave function manually on OVD data
  for(j in townums){
    print(j)
    sf_use_s2(FALSE)
    towlog <- read.table(paste0("Y:/Offshore/Assessment/Data/Survey_data/2022/Database loading/LE15/", i, "/", j, ".log"), skip=5)
    
    towlog$lon <- as.numeric(gsub(x=towlog$V2, pattern=",", replacement=""))
    towlog$lat <- as.numeric(gsub(x=towlog$V3, pattern=",", replacement=""))
    towlog$datetime <- paste0(towlog$V5, towlog$V4)
    towlog$datetime <- gsub(towlog$datetime, pattern=",", replacement ="")
    # OV is in UTC-3
    towlog$datetime <- dmy_hms(towlog$datetime)
    towlog$datetime <- towlog$datetime + hours(3)
    starttime <- towlog$datetime[1]
    endtime <- towlog$datetime[length(towlog$datetime)]
    towlog_raw <- towlog
    towlog$mave_lon <- mave(towlog$lon,w=c(1:10,9:1))
    towlog$mave_lat <- mave(towlog$lat,w=c(1:10,9:1))
    towlog <- towlog[seq(1, nrow(towlog), 2),]
    mave1 <- towlog[, c("mave_lon", "mave_lat", "datetime")] %>%
      st_as_sf(coords=c("mave_lon", "mave_lat"), crs=4326) %>%
      st_transform(32620) %>%
      group_by() %>%
      summarize(do_union=FALSE) %>%
      st_cast("LINESTRING") %>%
      st_transform(4326)
    
    mave1$tow <- j
    mave1$start <- starttime
    mave1$end <- endtime
    mave1$townum <- which(townums==j)
    mave1$length <- st_length(st_transform(mave1, 32620))
    mave1$dis <- 800/mave1$length
    
    towlog_raw <- towlog_raw[, c("lon", "lat", "datetime")] %>%
      st_as_sf(coords=c("lon", "lat"), crs=4326) %>%
      st_transform(32620) %>%
      group_by() %>%
      summarize(do_union=FALSE) %>%
      st_cast("LINESTRING") %>%
      st_transform(4326)
    
    towlog_raw$tow <- j
    towlog_raw$start <- starttime
    towlog_raw$end <- endtime
    towlog_raw$townum <- which(townums==j)
    towlog_raw$length <- st_length(st_transform(towlog_raw, 32620))
    towlog_raw$dis <- 800/towlog_raw$length
    
    ovd_mave <- rbind(ovd_mave, mave1)
    ovd_raw <- rbind(ovd_raw, towlog_raw)
    print(dim(ovd_mave))
    print(dim(ovd_raw))
  }
}

## looking at how old code works
# ovd <- dist.coef(#stringr::str_pad(1:200, width = 3, side = "left", pad = "0"), 
#                 tows=c(201:300), path="Y:/Offshore/Assessment/Data/Survey_data/2022/Database loading/LE15/LE15BBNlog/",w=c(1:10,9:1),rule=8,smooth=T,plt=F)
```


```{r, echo=F, include=F, eval=F} 
# Next we'll do the same to the Olex data, using sf and and the mave calculations
# I have to test out different mave parameters (time frames/windows), so I'm looping through 15 times. 
windows <- 5:20
olex_mave <- NULL
mave1 <- NULL
# this actually contains all middle and sable tracks too
tracks <- olex_import(filename="Y:/Offshore/Assessment/Data/Survey_data/2022/Database loading/LE15/GBBBNGERLE15.gz", ntows=212, type="track")
tracks_df <- as.data.frame(st_coordinates(tracks))
for(w in windows){
  for(i in 1:nrow(tracks)){
    sf_use_s2(FALSE)
    mave1 <- tracks_df[tracks_df$L1==i,]
    mave1$POS <- 1:nrow(mave1)
    
    mave1$mave_lon <- mave(mave1$X,w=c(1:w,(w-1):1))
    mave1$mave_lat <- mave(mave1$Y,w=c(1:w,(w-1):1))
    if(nrow(mave1)>2) mave1 <- mave1[seq(1, nrow(mave1), 2),]
    mave1 <- mave1[, c("mave_lon", "mave_lat")] %>%
      st_as_sf(coords=c("mave_lon", "mave_lat"), crs=4326) %>%
      st_transform(32620) %>%
      group_by() %>%
      summarize(do_union=FALSE) %>%
      st_cast("LINESTRING") %>%
      st_transform(4326)
    
    mave1$ID <- i
    mave1$length <- st_length(st_transform(mave1, 32620))
    mave1$dis <- 800/mave1$length
    mave1$window <- w
    
    olex_mave <- rbind(olex_mave, mave1)
  }
}

```


```{r, echo=F, include=F, eval=F}
# Create object and save
nav_obj <- list(tracks=tracks, olex_mave=olex_mave, ovd_raw=ovd_raw, ovd_mave=ovd_mave, ovd_track=ovd_track, ovd_se=ovd_se)

save(nav_obj, file = "C:/Users/keyserf/Documents/temp_data/nav_obj.RData")

```

```{r, echo=F, include=F}
# load object
load("C:/Users/keyserf/Documents/temp_data/nav_obj.RData")

tracks <- nav_obj$tracks
olex_mave <- nav_obj$olex_mave
ovd_raw <- nav_obj$ovd_raw
ovd_mave <- nav_obj$ovd_mave
ovd_track <- nav_obj$ovd_track
ovd_se <- nav_obj$ovd_se

```

```{r, echo=F, include=F}
# match olex tows to OV tows to get tow ID. Tows aren't always done in the order of their numbering.
sf_use_s2(FALSE)
tow_match <- st_nearest_feature(ovd_mave, olex_mave[olex_mave$window==min(olex_mave$window),])
ovd_mave$ID <- tow_match
ovd_raw$ID <- tow_match
joiner <- ovd_mave[,c("tow", "ID")]
st_geometry(joiner) <- NULL
olex_mave <- left_join(olex_mave, joiner)
names(tracks)[1] <- "ID"
tracks <- left_join(tracks, joiner)

tracks$L1 <- 1:nrow(tracks)
ovd_raw$L1 <- 1:nrow(ovd_raw)

ovd_pts <- as.data.frame(st_coordinates(ovd_raw)) %>%
  group_by(L1) %>%
  mutate(POS=1:n(), 
         L1=L1) %>%
  left_join(ovd_raw) %>%
  ungroup() %>%
  dplyr::select(-geometry) %>%
  group_by(tow) %>%
  st_as_sf(coords=c("X", "Y"), crs=4326) %>%
  filter(!is.na(tow))

olex_pts <- as.data.frame(st_coordinates(tracks)) %>%
  group_by(L1) %>%
  mutate(POS = 1:n(),
         L1=L1) %>%
  left_join(tracks) %>%
  ungroup() %>%
  dplyr::select(-geometry) %>%
  left_join(olex_mave) %>%
  ungroup() %>%
  dplyr::select(-geometry) %>%
  group_by(tow) %>%
  st_as_sf(coords=c("X", "Y"), crs=4326) %>%
  filter(!is.na(tow))

olex_mave <- olex_mave[!is.na(olex_mave$tow),]
tracks <- tracks[!is.na(tracks$tow),]
```

### Plot

Yellow is the raw Olex track. Red is the smoothed Olex track.    
Black is the raw OV track. Blue is the smoothed OV track.    
Raw Olex and OV _points_ were also plotted, but are not included here due to processing time.   
```{r, echo=F}
# plot em up, change tow number or window number to explore.
#towplot <- c(201)
towplot <- unique(tracks$tow)
g <- ggplot() + 
  geom_sf(data=tracks[tracks$tow %in% towplot,], aes(group=tow), lwd=4, colour="yellow") + 
  geom_sf(data=ovd_raw[ovd_raw$tow %in% towplot,], aes(group=tow), lwd=3, colour="black") + 
  geom_sf(data=ovd_mave[ovd_mave$tow %in% towplot,], aes(group=tow), lwd=2, colour="blue") +
  geom_sf(data=olex_mave[olex_mave$window==14 & olex_mave$tow %in% towplot,], aes(group=tow), colour="red") # +
  # geom_sf_text(data=olex_pts[olex_pts$tow %in% towplot,], aes(label=POS)) +
  # geom_sf_text(data=ovd_pts[ovd_pts$tow %in% towplot,], aes(label=POS), colour="pink") 
  #facet_wrap(~tow)
ggplotly(g, tooltip="tow")

```
Smoothed tows are shorter than raw tows. 


### Tow lengths (in distance and time)     
Distance first    
Using raw values      
```{r, echo=F}
tracks <- tracks %>%
  st_transform(32620) %>%
  mutate(length=st_length(.)) %>%
  st_transform(4326) 

rawlengthcomp <- as.data.frame(tracks) %>%
  dplyr::select(tow, length) %>%
  dplyr::mutate(length_olex=length) %>%
  dplyr::select(-length) %>%
  left_join(dplyr::select(as.data.frame(ovd_raw), tow, length), by="tow")

print("Raw olex length - raw OV length")
summary(rawlengthcomp$length_olex-rawlengthcomp$length)

ggplot() + geom_text(data=rawlengthcomp, aes(as.numeric(length_olex), as.numeric(length), label=tow)) +
  theme_bw() + theme(panel.grid=element_blank()) + xlab("olex length (m)") + ylab("OV length (m)") +
  geom_abline(aes(slope=1, intercept=0)) + ggtitle("Raw (before smoothing)")
```  

Raw OV tows are longer in distance than raw Olex tows.     

What happens when we smooth them though?     
Use the table to figure out the best moving average window for Olex (aim for prop=1 and diff=0)    
```{r, echo=F}
lengthcomp <- as.data.frame(olex_mave) %>%
  dplyr::select(tow, length, window) %>%
  dplyr::mutate(length_olex=length) %>%
  dplyr::select(-length) %>%
  left_join(dplyr::select(as.data.frame(ovd_mave), tow, length), by = "tow") %>%
  mutate(length_ovd = length) %>%
  select(-length)

lengthcomp %>%
  group_by(window) %>%
  summarize(olex_med = median(length_olex, na.rm=T), 
            ov_med = median(length_ovd, na.rm=T),
            diff_med = median(length_olex-length_ovd, na.rm=T),
            diff_min = min(length_olex-length_ovd, na.rm=T),
            diff_max = max(length_olex-length_ovd, na.rm=T),
            prop_med = median(length_olex/length_ovd, na.rm=T),
            prop_min = min(length_olex/length_ovd, na.rm=T),
            prop_max = max(length_olex/length_ovd, na.rm=T))

ggplot() + geom_point(data=lengthcomp, aes(as.numeric(length_olex), as.numeric(length_ovd))) +
  theme_bw() + theme(panel.grid=element_blank()) + xlab("olex length (m)") + ylab("OV length (m)") +
  geom_abline(data=lengthcomp, aes(slope=1, intercept=0)) + 
  ggtitle("After smoothing (faceted by smoothing parameter)") + 
  facet_wrap(~window)

ggplot() + geom_text(data=lengthcomp[lengthcomp$window==14,], aes(as.numeric(length_olex), as.numeric(length_ovd), label=tow)) +
  theme_bw() + theme(panel.grid=element_blank()) + xlab("olex length (m)") + ylab("OV length (m)") +
  geom_abline(data=lengthcomp, aes(slope=1, intercept=0)) + 
  ggtitle("After smoothing (for smoothing parameter of 14)") 

print("Summary of smoothed Olex length (smoothing parameter = 14) - smoothed OV length (smoothing parameter = 10)")
summary(lengthcomp$length_olex[lengthcomp$window==14]-lengthcomp$length_ovd)
print("Summary of smoothed Olex length (smoothing parameter = 14) / smoothed OV length (smoothing parameter = 10)")
summary(lengthcomp$length_olex[lengthcomp$window==14]/lengthcomp$length_ovd)

```

Check outlier tows in plotly above.      
Tows differ in length by up to 69m when Olex uses a smoothing parameter of 14.      
Tows differ in length by up to 8% when Olex uses a smoothing parameter of 14.    
Olex tows are generally shorter than OV tows.



Tow duration (time) comparison     
```{r, echo=F}
ovd_times <- select(ovd_mave, tow, start, end) %>%
  mutate(start_ov = start,
         end_ov = end) %>%
  select(-start, -end)

olex_times <- select(tracks, tow, start, end) %>%
  mutate(start_olex = start,
         end_olex = end) %>%
  select(-start, -end)

st_geometry(ovd_times) <- NULL
st_geometry(olex_times) <- NULL

times <- full_join(ovd_times, olex_times, by="tow")

# ggplot() + geom_point(data=times, aes(start_olex, start_ov)) + geom_abline(aes(slope=1, intercept=0))
# ggplot() + geom_point(data=times, aes(end_olex, end_ov)) + geom_abline(aes(slope=1, intercept=0))

# had to do a manual fix to some Middle Bank tows that were on the wrong day in OV?
times[as.numeric(times$tow) %in% 5:15,]$start_ov <- times[as.numeric(times$tow) %in% 5:15,]$start_ov + days(1)
times[as.numeric(times$tow) %in% 5:15,]$end_ov <- times[as.numeric(times$tow) %in% 5:15,]$end_ov + days(1)

times$diff <- times$start_olex-times$start_ov

# ggplot() + geom_text(data=times[times$start_ov<"2022-05-23",], aes(start_olex, start_ov, label=tow)) +
#   geom_abline(aes(slope=1, intercept=0))
# 
# ggplot() + geom_text(data=times[times$start_ov<"2022-05-23",], aes(tow, start_olex), label="olex") + 
#   geom_text(data=times[times$start_ov<"2022-05-23",], aes(tow, start_ov), label="ov")

# ggplot() + geom_text(data=times, aes(tow, y=start_ov-start_olex, label=tow))
print("Start_ov - Start_olex in seconds")
summary(as.numeric(times$start_ov) - as.numeric(times$start_olex))
# Olex was started 5 seconds EARLIER (median)
print("End_ov - End_olex in seconds")
summary(as.numeric(times$end_ov) - as.numeric(times$end_olex))
# Olex was ended 2 seconds EARLIER (median)

times$duration_ov <- times$end_ov-times$start_ov
times$duration_olex <- times$end_olex-times$start_olex

ggplot() + geom_text(data=times, aes(as.numeric(duration_olex), as.numeric(duration_ov), label=tow)) +
  geom_abline(aes(slope=1, intercept=0)) + theme_bw() + theme(panel.grid=element_blank()) +
  xlab("Duration of Olex tow (minutes)") + 
  ylab("Duration of OV tow (minutes)")

print("Summary of olex duration")
summary(as.numeric(times$duration_olex))
print("Summary of OV duration")
summary(as.numeric(times$duration_ov))

times <- times %>% select(tow, duration_olex, duration_ov, diff) %>%
  pivot_longer(!tow)

ggplot() + geom_line(data=times[!times$name=="diff",], aes(x=tow, y=as.numeric(value)/60, colour=name, group=name)) + 
  theme_bw() + theme(panel.grid=element_blank()) +
  scale_colour_manual(name="System", labels=c("Olex", "OV"), values=c("red", "blue"))+
  ylab("Duration of tow (minutes)")

# ggplot() + geom_point(data=times, aes(x=tow, y=as.numeric(duration_olex)), colour="red") + 
#   geom_point(data=times, aes(x=tow, y=as.numeric(duration_ov), group=1), colour="blue") 
```       

Raw olex tows were longer in time duration than raw OV tows.         
Olex was started 5 seconds earlier (median).    
Olex was ended 2 seconds earlier (median).     


### Number of points logged by each system     
```{r, echo=F, message=F}
pt_sum <- olex_pts %>%
  group_by(ID,tow) %>%
  summarize(npoints_olex = max(POS))

print("Summary of number of points for Olex")
summary(pt_sum$npoints_olex)

pt_sum <- as.data.frame(ovd_pts) %>%
  group_by(tow) %>%
  summarize(npoints_ov = max(POS)) %>%
  left_join(as.data.frame(pt_sum), by="tow")
# Olex is polling more frequently, and ov often has 189 records? Huh? Why...

print("Summary of number of points for OV")
summary(pt_sum$npoints_ov)

#ggplot() + geom_histogram(data=pt_sum, aes(npoints_ov), binwidth=1)
#ggplot() + geom_histogram(data=pt_sum, aes(npoints_olex), binwidth=1)

pts_olex <- left_join(olex_mave, data.frame(tow=pt_sum$tow, npoints_olex=pt_sum$npoints_olex), by="tow")
pts_tracks <- left_join(tracks, data.frame(tow=pt_sum$tow, npoints_olex=pt_sum$npoints_olex), by="tow")
pts_tracks$length <- st_length(pts_tracks)
pts_ov <- left_join(ovd_mave, data.frame(tow=pt_sum$tow, npoints_ov=pt_sum$npoints_ov), by="tow")
pts_ov_before <- left_join(ovd_raw, data.frame(tow=pt_sum$tow, npoints_ov=pt_sum$npoints_ov), by="tow")

olex_comp <- full_join(data.frame(tow=pts_tracks$tow, raw_length = pts_tracks$length, npoints_olex=pts_tracks$npoints_olex),
                       data.frame(tow=pts_olex$tow, window=pts_olex$window, smooth_length = pts_olex$length, npoints_olex=pts_olex$npoints_olex), by=c("tow", "npoints_olex"))

olex_comp$diff <- olex_comp$raw_length - olex_comp$smooth_length

ggplot() + geom_point(data=pts_tracks, aes(as.numeric(length), npoints_olex)) + ggtitle("Olex before smoothing") + xlab("Length before smoothing")
ggplot() + geom_point(data=pts_olex, aes(as.numeric(length), npoints_olex)) + ggtitle("Olex after smoothing") + facet_wrap(~window) + xlab("Length after smoothing")
ggplot() + geom_point(data=pts_ov_before, aes(as.numeric(length), npoints_ov)) + ggtitle("OV before smoothing") + xlab("Length before smoothing")
ggplot() + geom_point(data=pts_ov, aes(as.numeric(length), npoints_ov)) + ggtitle("OV after smoothing")
ggplot() + geom_point(data=olex_comp, aes(as.numeric(diff), npoints_olex)) + ggtitle("Difference between Olex before and after smoothing") + facet_wrap(~window)
```      

OV almost always record 190 points for a tow, whereas Olex is much more variable.    


### Historical distance coefficients from SCALOFF     
```{r, echo=F, include=F, eval=F}
source("C:/Users/keyserf/Documents/Github/Assessment_fns/Other_functions/ScallopQuery.R")
dis_hist <- ScallopQuery("ROracle", db.con="ptran", SQLtext = "Select * from SCALOFF.OSTOWS")
head(dis_hist)
require(lubridate)
dis_hist$year <- year(ymd_hms(dis_hist$TOW_DATE))

dis_hist_means <- dis_hist %>%
  group_by(year) %>%
  summarize(mean_dis_coef = mean(DIS_COEF),
            sd_dis_coef = sd(DIS_COEF))

ggplot() + geom_point(data=dis_hist, aes(ymd_hms(TOW_DATE), DIS_COEF, colour=as.factor(TECH_ID), shape=as.factor(DIS_COEF_ID)))

ggplot() + geom_point(data=dis_hist[dis_hist$year==2016,], aes(ymd_hms(TOW_DATE), DIS_COEF, colour=as.factor(TECH_ID), shape=as.factor(DIS_COEF_ID)), alpha=0.5)

ggplot() + geom_boxplot(data=dis_hist, aes(year, DIS_COEF, group=year), outlier.shape=NA) + ylim(0.3,1.3)

ggplot() + geom_point(data=dis_hist_means, aes(year, mean_dis_coef))

# check dis_coef_id
ggplot() + geom_point(data=dis_hist, aes(ymd_hms(TOW_DATE), DIS_COEF_ID))
```


Observations from Trish:      
 - GPS could be off by 1 hundredth. Olex has a separate feed (not a splitter).   
 - We had a freezing issue last year when we tried to use a splitter.    
 - TPD has nautical miles for each tow in Olex.    
 - Speeds varied between systems too.    
 - Slight difference in vessel location between olex and OV, noticed when "on station"      
 - OV starts first, timer, then olex      
 - 3 second intervals for OV      
 - Also have data on warp length (fathoms)     

